\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Khaled,
    middleinitial=A,
    lastname=Ibrahim,
    email=khaledelbalal@gmail.com,
    phone=(+20)1020922021,
    linkedin=KhaledElbalal,
    %github=KhaledElbalal,
    %city=Giza,
    %state=EG
]

\vspace{0.25in}
\today
\vspace{0.15in}


Dear Hiring Manager,

I am writing to express my strong interest in the Associate Consultant Intern position at MasterCard, specifically within the Performance Analytics track. As a data science student with a deep passion for analytics and a profound understanding of business, I am excited about the opportunity to contribute my skills and knowledge to this dynamic role.

The Performance Analytics track at MasterCard aligns perfectly with my
background and aspirations. I have experience working with diverse
datasets and leveraging analytical techniques to generate actionable
insights. Through coursework and practical projects, I have honed my
skills in data analysis, using tools such as Hadoop, Python, Pandas, NumPy and more to
synthesize complex data into clear recommendations. I am particularly
drawn to the challenge of helping clients answer questions related to
metrics, market share, and competitive positioning, as this aligns with
my analytical aptitude and problem-solving skills.

Thank you for taking the time to review my application. I look forward
to hopefully meeting with you in the future to further discuss my
qualifications for a position as an Associate Consultant at MasterCard
this upcoming summer. If you have any questions, please feel free to
email me at \href{mailto:khaledelbalal@gmail.com}{khaledelbalal@gmail.com} or
call me at \href{tel:+20-102-092-2021}{+20-102-092-2021}.

Sincerely,

\vspace{.15in}

Khaled Ibrahim

\end{document}