\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Khaled,
    middleinitial=A,
    lastname=Ibrahim,
    email=khaled.elbalal@gmail.com,
    phone=(+20)102 092 2021,
    website=khaled.works,
    linkedin=khaledelbalal,
    github=khaledelbalal,
    city=Giza,
    state=EG,
    fixobjectivespacing=true
]
% ----- Education -----
\section{Education}

\experience{Bachelor of Science}{Data Science}{Oct 2021}{June 2025}{
    \noindent Faculty of Computers \& AI \hfill GPA: 3.74 \newline
    Cairo University, Giza, Egypt
    \newline
    \textbf{Relevant Coursework:} Machine Learning - Introduction to Data Science
    - Mathematical Optimization - Operating Systems \newline Database Management \& Warehousing -
    Fundamentals of Software Engineering
    - Algorithms Design \& Analysis
}

% ----- Work Experience -----
\section{Work Experience}

\experience{Intern}{Nestle Business Services}{July 2023}{September 2023
    -- Cairo, Egypt}{
    \achievement{
        Contributed to the initial exploration of AI solutions for Nestle's
        H2R Contact Center.
    }
    \achievement{
        Conducted in-depth research on various machine learning models,
        including advanced language and text-embedding models.
    }
    \achievement{
        Deployed a demo AI-powered application, leveraging Python, Eel,
        PyInstaller,
        Sentence Embeddings, and PyTorch.
    }
}

\experience{Junior Web Developer}{Syncore LLC}{September 2019}{August
    2022 -- Remote}{
    \achievement{
        Focused on writing clean, well-documented code to ensure maintainability and scalability.
    }
    \achievement{
        Utilized the best suited technologies for each project, which allowed us to achieve average
        Lighthouse scores of 97\%+.
    }
    \achievement{
        Actively engaged in the design process, collaborating with designers
        and clients  to create user-friendly and intuitive web pages.
    }
}


% ----- Technical Projects -----
\section{Technical Projects}

\githubexperience{Representing \& Verifying Workflow Nets Using C++}{Project}{March
    2023}{Feb 2024}{
    \achievement{
        Translated complex mathematical concepts into practical C++ implementations for business process analysis.
    }
    \achievement{
        Programmatically Created SVGs to develop clear visualizations of Petri Net systems.
    }
    \achievement{
        Engineered and deployed an efficient C++ backend on Microsoft Azure.
    }
    \achievement{
        Deployed a \underline{\href{https://netlify.app}{user-friendly ReactJS frontend}}, allowing users to interact with the application and visualize the results.
    }
}{https://github.com/KhaledElbalal/workflow-net-representation/}

\githubexperience{Analyzing Walmart Weekly Sales}{University Assignment}{May
    2023}{June 2023}{
    \achievement{
        Executed a detailed \underline{\href{https://github.com/KhaledElbalal/SIS213-Weekly-Sales-Prediction/blob/main/Data\%20Science\%20Report.pdf}{Exploratory Data Analysis}}, uncovering critical patterns and trends across 3+ key metrics.
    }
    \achievement{
        Developed multiple machine learning models to predict weekly sales, including Linear Regression, Random Forest, and XGBoost.
    }
    \achievement{Using multiple criteria, performed model selection to choose the best model suited for the underlying problem.
    }
}{https://github.com/KhaledElbalal/SIS213-Weekly-Sales-Prediction/}

\githubexperience{Polynomial Differentiation using Linear Algebra}{Project}{July 2022}{August 2022}{
    \achievement{
        Wrote a custom parsing algorithm to convert a polynomial expression into a matrix.
    }
    \achievement{
        Implemented a differentiation algorithm using the matrix representation of the polynomial.
    }
    \achievement{
        Developed a \underline{\href{https://netlify.app}{user-friendly frontend}} using KaTeX, HTML and TailwindCSS to display the results.
    }
}{https://github.com/KhaledElbalal/polynomialDerivative}


\githubexperience{Diabetes Prediction using Classical ML}{Project}{April 2022}{May 2022}{
\achievement{
    Collaborated with pharmacists, doctors, and subject matter experts to deepen my understanding of the data and intricacies of the problem during the Exploratory Data Analysis (EDA) phase.
}
\achievement{
    Conducted thorough data cleaning and feature engineering to enhance machine learning model performance.
}
\achievement{
    Implemented and finely tuned a Logistic Regression classifier, achieving an accuracy rate of over 90\%.
}
\achievement{
    Developed and deployed a \underline{\href{https://netlify.app}{simple application}} powered by a \underline{\href{https://netlify.app}{Flask backend}} on Microsoft Azure.
    }
}{https://github.com/KhaledElbalal/modelDeployment}

\section{Volunteering}

\experience{Research \& Documentation Member}{MIOM FEPS-CU}{Jan 2023}{Present}{
    \achievement{
        Authoring comprehensive reports on leveraging existing data for
        migration research, contributing to the strategic understanding of
        migration patterns and trends in light of the Sustainable
        Developement Goals (SDGs).
    }
}

\experience{Competitive Programming Mentor}{ICPC FCAI-CU}{April
    2023}{August 2023}{
    \achievement{
        Managed a group of 20+ students in Competitive Programming for the ICPC community.
    }
    \achievement{
        Facilitated weekly up-solving sessions, empowering team members to tackle 3-5 complex programming problems.
    }
    \achievement{
        Exhibited proficiency in C++ and Data Structures while instructing team members on solving programming challenges.
    }
}


% ----- Skills -----
\section{Skills}

\normalsize{
    \noindent \tech{Programming Languages \& Tools:} Python - SQL - NoSQL - C/C++ - TypeScript
    - JavaScript - Git - Docker

    \noindent \tech{Data Science:} NumPy - Pandas - Matplotlib - Seaborn
    - TensorFlow/Keras - PyTorch

    \noindent \tech{Web Technology:} Docker - ReactJS - NextJS - Firebase - Microsoft Azure - TailwindCSS

    \noindent \tech{Soft Skills:} Analytical Thinking - Leadership - Communication - Time Management}

\end{document}
